---
title: 'DS 621 Fall2020: Final Project (Group3)'
subtitle: 'CO2 Emissions Regression'
author: 'Zach Alexander, Sam Bellows, Donny Lofland, Joshua Registe, Neil Shah, Aaron Zalki'
data: '11/20/2020'
output:
  html_document:  
    theme: cerulean
    highlight: pygments
    css: https://raw.githubusercontent.com/djlofland/DS621_F2020_Group3/master/Homework_4/lab.css
    toc: true
    toc_float: true
  pdf_document:
    extra_dependencies: ["geometry", "multicol", "multirow", "xcolor"]
---


Source code: [https://github.com/djlofland/DS621_F2020_Group3/tree/master/Final%20Project](https://github.com/djlofland/DS621_F2020_Group3/tree/master/Final%20Project)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(MASS)
library(scales)
library(rpart.plot)
library(ggplot2)
library(ggfortify)
library(gridExtra)
library(forecast)
library(fpp2)
library(fma)
library(kableExtra)
library(e1071)
library(mlbench)
library(ggcorrplot)
library(DataExplorer)
library(timeDate)
library(caret)
library(GGally)
library(corrplot)
library(RColorBrewer)
library(tibble)
library(tidyr)
library(tidyverse)
library(tidyselect)
library(dplyr)
library(reshape2)
library(mixtools)
library(tidymodels)
library(ggpmisc)
library(regclass)
library(pROC)
library(skimr)
library(naniar)
library(RANN)
library(kableExtra)
#' Print a side-by-side Histogram and QQPlot of Residuals
#'
#' @param model A model
#' @examples
#' residPlot(myModel)
#' @return null
#' @export
residPlot <- function(model) {
  # Make sure a model was passed
  if (is.null(model)) {
    return
  }
  
  layout(matrix(c(1,1,2,3), 2, 2, byrow = TRUE))
  plot(residuals(model))
  hist(model[["residuals"]], freq = FALSE, breaks = "fd", main = "Residual Histogram",
       xlab = "Residuals",col="lightgreen")
  lines(density(model[["residuals"]], kernel = "ep"),col="blue", lwd=3)
  curve(dnorm(x,mean=mean(model[["residuals"]]), sd=sd(model[["residuals"]])), col="red", lwd=3, lty="dotted", add=T)
  qqnorm(model[["residuals"]], main = "Residual Q-Q plot")
  qqline(model[["residuals"]],col="red", lwd=3, lty="dotted")
  par(mfrow = c(1, 1))
}
#' Print a Variable Importance Plot for the provided model
#'
#' @param model The model
#' @param chart_title The Title to show on the plot
#' @examples
#' variableImportancePlot(myLinearModel, 'My Title)
#' @return null
#' @export
variableImportancePlot <- function(model=NULL, chart_title='Variable Importance Plot') {
  # Make sure a model was passed
  if (is.null(model)) {
    return
  }
  
  # use caret and gglot to print a variable importance plot
  varImp(model) %>% as.data.frame() %>% top_n(n = 6) %>% 
    ggplot(aes(x = reorder(rownames(.), desc(Overall)), y = Overall)) +
    geom_col(aes(fill = Overall)) +
    theme(panel.background = element_blank(),
          panel.grid = element_blank(),
          axis.text.x = element_text(angle = 90)) +
    scale_fill_gradient() +
    labs(title = chart_title,
         x = "Parameter",
         y = "Relative Importance")
}
#' Print a Facet Chart of histograms
#'
#' @param df Dataset
#' @param box Facet size (rows)
#' @examples
#' histbox(my_df, 3)
#' @return null
#' @export
histbox <- function(df, box) {
    par(mfrow = box)
    ndf <- dimnames(df)[[2]]
    
    for (i in seq_along(ndf)) {
            data <- na.omit(unlist(df[, i]))
            hist(data, breaks = "fd", main = paste("Histogram of", ndf[i]),
                 xlab = ndf[i], freq = FALSE)
            lines(density(data, kernel = "ep"), col = 'red')
    }
    
    par(mfrow = c(1, 1))
}
#' Extract key performance results from a model
#'
#' @param model A linear model of interest
#' @examples
#' model_performance_extraction(my_model)
#' @return data.frame
#' @export
model_performance_extraction <- function(model=NULL) {
  # Make sure a model was passed
  if (is.null(model)) {
    return
  }
  
  data.frame("RSE" = model$sigma,
             "Adj R2" = model$adj.r.squared,
             "F-Statistic" = model$fstatistic[1])
}
#' Initial cleaning of the dataset
#'
#' @dataset dataset being cleaned, specific to insurance datasets
#' @return data.frame
#' @export
initial_cleaning<- function(dataset){
  
  dataset<-dataset %>% 
    dplyr::select(-INDEX) %>% 
    #converting the currency based columns to numeric
    mutate_at(vars(c("INCOME","HOME_VAL","OLDCLAIM","BLUEBOOK")),~as.numeric(str_replace_all(.,c("\\$"="","\\,"="")))) %>% 
    mutate_at(vars("TARGET_FLAG"),as.factor)
  
  return(dataset)
}
```

## Abstract

250 words or less

## Introduction

Include background and motivation of problem

```{r}
kaggledf<-read.csv("https://raw.githubusercontent.com/djlofland/DS621_F2020_Group3/master/Final%20Project/datasets/Kaggle%20CO2/CO2%20Emissions_Canada.csv")
```

## Methodology

### Summary Stats

```{r}
skim(kaggledf)
```



### Distributions

```{r fig.height=10, fig.width=14}
DataExplorer::plot_bar(
  data = kaggledf,
         order_bar = T,
         ggtheme=theme_bw())
```


```{r, echo=FALSE}
DataExplorer::plot_histogram(
  geom_histogram_args = list(alpha = 0.5),
   data = kaggledf,
         ggtheme=theme_bw())
```



### Boxplots

```{r}
# Prepare data for ggplot
gather_df <- kaggledf %>% select(CO2.Emissions.g.km., Engine.Size.L., Fuel.Consumption.City..L.100.km., Fuel.Consumption.Hwy..L.100.km., Fuel.Consumption.Comb..L.100.km., Fuel.Consumption.Comb..mpg.) %>% 
  gather(key = 'variable', value = 'value')

# Histogram plots of each variable
ggplot(gather_df) + 
  geom_histogram(aes(x=value, y = ..density..), bins=30) + 
  geom_density(aes(x=value), color='blue') +
  facet_wrap(. ~variable, scales='free', ncol=3)
```





### Variable Plots

```{r}
DataExplorer::plot_scatterplot(
    data = dplyr::select_if(kaggledf,is.numeric),
    by = "CO2.Emissions.g.km.",
         ggtheme=theme_bw(),
    theme_config = list(axis.text.x = element_text(angle = 90)))
```



### Data Sparsity Check

```{r}
DataExplorer::plot_missing(kaggledf, ggtheme = theme_bw())
#gg_miss_upset(kaggledf)
```

### Data Preparation



### Removed Fields



### Near Zero Variance



### Outliers





### Transform non-normal variables

```{r}
# separate our features from target so we don't inadvertently transform the target
training_x <- kaggledf %>% select(-CO2.Emissions.g.km., -Make, -Model, -Vehicle.Class, -Cylinders, -Transmission, -Fuel.Type)
training_y <- kaggledf$CO2.Emissions.g.km.

training_disc <- kaggledf %>% select(Make, Model, Vehicle.Class, Cylinders, Transmission, Fuel.Type)

imputation <- preProcess(training_x, method = c('BoxCox'))

training_x_imp <- predict(imputation, training_x)

temp_df <- cbind(training_y, training_x_imp) %>%
  as.data.frame() %>%
  rename(TARGET = training_y)

histbox(temp_df, c(3, 2))
```



```{r}
# Calculate and plot the Multicolinearity
correlation = cor(temp_df, use = 'pairwise.complete.obs')

corrplot(correlation, 'ellipse', type = 'lower', order = 'hclust',
         col=brewer.pal(n=8, name="RdYlBu"))
```


```{r}
cleandf <- transform(merge(temp_df, training_disc, by=0 ,all=TRUE), row.names=as.numeric(Row.names), Row.names=NULL)
cleandf <- cleandf[order(as.numeric(rownames(cleandf))),,drop=FALSE]

# removing these features for now since there are to many groupings
cleandf <- cleandf %>% select(-Make, -Model)
```


## Experimentation & Results

### Modeling

```{r}
set.seed(123456)
```

```{r}
# utilizing one dataset for all four models
cleaneddfTrain <- createDataPartition(cleandf$TARGET, p=0.8, list=FALSE)
cleaneddftraining <- cleandf[cleaneddfTrain,]
cleaneddftesting <- cleandf[-cleaneddfTrain,]
```

### Just to show that Engine Size and Fuel Consumption are quite predictive of gas emissions
```{r}
model1 <- lm(TARGET ~ ., data = temp_df)
summary(model1)
```

### For an initial linear model we'll include everything

```{r}
model2 <- lm(TARGET ~ ., data = cleaneddftraining)
summary(model2)
```

```{r}
# Build model 2 - this is Model 1 with only significant features (using stepAIC)
model3 <- stepAIC(model2, direction = "both",
                         scope = list(upper = model2, lower = ~ 1),
                         scale = 0, trace = FALSE)
# Display Model 2 Summary
(model3_summary <- summary(model3))
```


## Conclusion

## References & Appendices
